% !TeX root = ../main.tex

\begin{abstract}
  论文的摘要是对论文研究内容和成果的高度概括。
  摘要应对论文所研究的问题及其研究目的进行描述，对研究方法和过程进行简单介绍，
  对研究成果和所得结论进行概括，突出论文的创新之处。
  摘要应具有独立性和自明性，其内容应包含与论文全文同等量的主要信息。
  使读者即使不阅读全文，通过摘要就能了解论文的总体内容和主要成果。

  论文摘要的书写应力求精确、简明，不宜使用公式、图表，不引用文献。
  切忌写成对论文书写内容进行提要的形式，尤其要避免“第 1 章……；第 2 章……；……”
  这种或类似的陈述方式。

  本文的创新点主要有：
  \begin{itemize}
    \item 用例子来解释模板的使用方法；
    \item 用废话来填充无关紧要的部分；
    \item 一边学习摸索一边编写新代码。
  \end{itemize}

  关键词是为了文献标引工作、用以表示全文主要内容信息的单词或术语。
  关键词不超过 5 个，每个关键词中间用分号分隔。
  英文摘要的关键词与中文摘要的关键词应完全一致。

  \keywords{学位论文；\LaTeX{}；模板}
\end{abstract}

\begin{enabstract}
  An abstract of a dissertation is a summary and extraction of research work
  and contributions.
  Included in an abstract should be description of research topic and research
  objective, brief introduction to methodology and research process, and
  summarization of conclusion and contributions of the research.  An abstract
  should be characterized by independence and clarity and carry identical
  information with the dissertation.
  It should be such that the general idea and major contributions of the
  dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point.
  It is a misunderstanding to make an abstract an outline of the dissertation
  and words ``the first chapter'', ``the second chapter'' and the like should
  be avoided in the abstract.

  Key words are terms used in a dissertation for indexing, reflecting core
  information of the dissertation.
  An abstract may contain a maximum of 5 key words, with semi-colons used in
  between to separate one another.

  \enkeywords{Dissertation; \LaTeX{}; template}
\end{enabstract}
